
---
title: "Bycatch Data Submission"
author: "Lobster Group, Science Branch "
output: tint::tintPdf
bibliography: references.bib
---


**1. Data was collected**
```{r echo =FALSE, message =FALSE, error = FALSE, warning = FALSE, results='asis' , fig-main, fig.width=10, fig.height=12,  cache=TRUE,}
  
    dat$Y<- convert.dd.dddd(dat$LATDDMM, format="dec.deg")
    dat$X<- convert.dd.dddd(dat$LONGDDMM, format="dec.deg")*-1
    dat$EID<- 1:nrow(dat)

    xlim = c(min(dat$X,na.rm=T)-0.5, max(dat$X,na.rm=T)+0.5)
    ylim = c(min(dat$Y,na.rm=T)-0.5, max(dat$Y,na.rm=T)+0.5)
   
    LobrMap(ylim=ylim ,xlim=xlim, coast=coa,LFAs=lfas)
    attr(dat,"projection") <- "LL"
    addPoints(na.omit(dat[,c('X','Y','EID')]), pch = 21, cex=1.5, bg='red')

    ll<-unique(dat$COMAREA_ID)
    lll<-ifelse(nchar(ll)==3,3,4)
    ll<-substr(ll,2,lll)
    title(paste0("LFA", ll))
```

**2. What group entered the data and the name of the data file that was imported**
```{r  echo=FALSE, results = 'asis'}
cat(paste(" ", unique(dat$OWNER_GROUP), unique(dat$TRIP), " "))  
if(!grepl(unique(dat$TRIP), nm)){
  cat(paste(" \\textcolor{red}{Trip File Name does not match TRIP column in Data Sheet. Check ", Fi[i], "} ", sep=" "))
}

``` 

**3. Does the Trip Name match the licence Number**
```{r  echo=FALSE, results = 'asis'}

# Extract the part before the hyphen and remove leading zeros
dat$TRIP_PREFIX <- sub("^0+", "", sub("-.*", "", dat$TRIP))

# Check if TRIP_PREFIX matches LICENSE_NO
dat$match <- dat$TRIP_PREFIX == dat$LICENSE_NO

# Filter out mismatched rows
mismatch_data <- dat[dat$match == FALSE, ]

# Output results
if (nrow(mismatch_data) > 0) {
  cat("\\textcolor{red}{No: Trip name does not match the license number.}")
} else {
  cat("\\textcolor{black}{Yes: All trip names match the license numbers.}")
}

```

**4. Does the Trip Name match the Boarding Date**
```{r echo=FALSE, results = 'asis'}
# Ensure BOARD_DATE is in Date format
dat$BOARD_DATE <- as.Date(dat$BOARD_DATE, format = "%Y-%m-%d")

# Extract the date part from TRIP
dat$TRIP_DATE <- sub(".*-", "", dat$TRIP)

# Format BOARD_DATE to match the format in TRIP_DATE
dat$BOARD_DATE_FORMATTED <- format(dat$BOARD_DATE, "%d%m%y")

# Check for mismatches
dat$date_match <- dat$TRIP_DATE == dat$BOARD_DATE_FORMATTED
date_mismatch_data <- dat[dat$date_match == FALSE, ]

# Print results using LaTeX for coloring
if (nrow(date_mismatch_data) > 0) {
  cat("\\textcolor{red}{No: Trip name does not match the boarding date.}")
} else {
  cat("\\textcolor{black}{Yes: Trip name matches the boarding date.}")
}
```

**5. Is the Number Hook Haul column populated? Can't be NA.**
```{r echo=FALSE, results = 'asis'}
na_indices <- which(is.na(dat$NUM_HOOK_HAUL))


if (length(na_indices) > 0) {
  cat("\\textcolor{red}{NUM HOOK HAUL Can't have NA, check lines: ", paste(na_indices, collapse = ", "), "}")
} else {
  cat("\\textcolor{black}{Number Hook Haul values are good}")
}
```

**6. Are Fish Numbers duplicated? **
```{r  echo=FALSE, results = 'asis'}
duplicated_fish_no <- dat$FISH_NO[duplicated(dat$FISH_NO)]

if (length(duplicated_fish_no) > 0) {
  cat("\\textcolor{red}{Values in FISH NO are repeated check fish number(s) are unique in data: ", paste(unique(duplicated_fish_no), collapse = ", "), "}")
} else {
  cat("\\textcolor{black}{No duplicated fish numbers}")
}
```

**7. Are Soak Days within reasonable range?**
```{r  echo=FALSE, results = 'asis'}
high_soak_days <- which(dat$SOAK_DAYS >= 15)

if (length(high_soak_days) > 0) {
  cat("\\textcolor{orange}{Soak Days are high, double check data sheet to ensure values are correct. Check Lines: ", paste(high_soak_days, collapse = ", "), "}")
} else {
  cat("\\textcolor{black}{SOAK DAYS values are within the normal range}")
}
```

 **8. Do the coordinates match the Grids and LFA?**
```{r  echo=FALSE, results = 'asis'}
    dat$COMAREA_ID[which(dat$COMAREA_ID =="L31A")]<-311
    dat$COMAREA_ID[which(dat$COMAREA_ID =="L31B")]<-312

    ll=unique(dat$COMAREA_ID)

    if(!unique(dat$COMAREA_ID) %in% c(311,312)){
        ll<-unique(dat$COMAREA_ID)
        lll<-ifelse(nchar(ll)==3,3,4)
        ll<-substr(ll,2,lll)
    }

    LFAs<-subset(LFAS, PID ==ll )
   LFAgrid<-subset(LFAGrid, PID == ll)


    #Convert to Decimal Degrees
    dat$Y<-convert.dd.dddd(dat$LATDDMM, format="dec.deg")
    dat$X<-(convert.dd.dddd(dat$LONGDDMM, format="dec.deg")*-1)
     
    dat$EID = 1:nrow(dat)

    #Check LFA Locations
    locCheck = NULL
   if(all(!is.na(dat$X))) locCheck<-findPolys(dat, LFAs)
    if(is.null(locCheck)){
        cat(paste0("<br> <ul> \textcolor{red}{ERROR:Wrong LFA identified} </br> </ul>"))
          }else{      
        missingLoc<-merge(dat, locCheck, all.x = T, by = "EID")
        missedLoc<-subset(missingLoc, is.na(PID))

        if(nrow(missedLoc)>0){ 
            print(paste0("<br> <ul> \textcolor{red}{ERROR:LFA locations missing or incorrect. Check line(s)",paste(as.numeric(row.names(missedLoc))+1, collapse=" , "),"}", sep=" ", "</br> </ul>"))
          } else {print("<br> <ul> <center> All locations match LFA </br> </ul> </center>")
        }
    #Check Grid Locations
    glocCheck<-findPolys(dat, LFAgrid)

    #Find missing grid locations - or locations that don't pair with corresponding grids
        missingGLoc<-merge(dat, glocCheck, all.x = T, by = "EID")
        missedGLoc<-subset(missingGLoc, is.na(PID))

    if(nrow(missedGLoc)>0){ 
          print(paste0("<br> <ul> \textcolor{red}{ERROR: Grid locations missing or incorrect. Check line(s) ", paste(as.numeric(row.names(missedGLoc))+1,collapse=","), "}", sep=" ", "</br> </ul>"))
        } else {cat("<br> <ul> All locations match grids </br> </ul>")
      }
    }
      
```
 
**9. Are males berried or notched?**
```{r echo=FALSE, results = 'asis'}
    dat$SEXCHECK<-NA
    dat$SEXCHECK<- ifelse(dat$SPECCD_ID ==2550 & dat$SEXCD_ID == 1 & !is.na(dat$VNOTCH) , 1, dat$SEXCHECK)
      
    notchcheck<-any(dat$SEXCHECK == 1, na.rm = T)
    notchmales<-which(dat$SEXCHECK == 1)


    if(notchcheck == T){
      print(paste0("<br> <ul> \textcolor{red}{ERROR:Check SEX and NOTCH. Errors on line(s) ",paste(notchmales+1, collapse=" , "), "}", sep=" ", "</br> </ul>"))
      }else {cat("<br> <ul> No Males are V-notched </br> </ul>")
      }
    dat$SEXCHECK <- NULL
```

**10. Is the length between a reasonable size 30-250mm?**
```{r echo=FALSE, results = 'asis'}

    dat$CLCHECK<-NA
    dat$CLCHECK<- ifelse(dat$SPECCD_ID == 2550 & (dat$FISH_LENGTH <=30 | dat$FISH_LENGTH >=250), 1, dat$CLCHECK)

    sizecheck<-any(dat$CLCHECK ==1, na.rm=T)
    wrongsize<-which(dat$CLCHECK==1)

    if(sizecheck == T){
      print(paste0("<br> <ul> \textcolor{red}{ERROR: Sizes are not reasonable. Check for errors on line(s) ", paste(wrongsize+1, collapse=" , "), "}", sep= " ", "</br> </ul>"))
    }else{cat("<br> <ul> Carapace sizes reasonable </br> </ul>")}

    dat$CLCHECK <- NULL 
      
```


**11. Is Length, Shell, Disease, Sex and Condition recorded for all Lobster?** 
```{r echo=FALSE, results = 'asis'}

    dat$LENGTHDAT<-NA
    dat$LENGTHDAT<-ifelse(dat$SPECCD_ID == 2550 & is.na(dat$FISH_LENGTH), 1, dat$LENGTHDAT)
    lengthcheck<-any(dat$LENGTHDAT == 1, na.rm=T)
    nolength<-which(dat$LENGTHDAT==1)
    if(lengthcheck == T){
      print(paste0("<br> <ul> \textcolor{red}{ERROR: Missing information for carapace length. Check line(s) ", paste(nolength+1, collapse=" , "), "}", sep=" ",  "</br> </ul>"))
    }else{ cat("<br> <ul> Carapace lengths recorded </br> </ul> ")
    }

    dat$SHELLDAT<-NA
    dat$SHELLDAT<-ifelse(dat$SPECCD_ID == 2550 & is.na(dat$SHELL), 1, dat$SHELLDAT)
    shellcheck<-any(dat$SHELLDAT == 1, na.rm=T)
    noshell<-which(dat$SHELLDAT==1)
    if(shellcheck == T){
      print(paste0("<br> <ul> \textcolor{red}{ERROR: Missing information for shell hardness. Check line(s) ", paste(noshell+1, collapse=" , "),"}", sep = " ", "</br> </ul>"))
    }else{ cat("<br> <ul> Shell hardness recorded </br> </ul>")
    }

    dat$SICDAT<-NA
    dat$SICDAT<-ifelse(dat$SPECCD_ID == 2550 & is.na(dat$DISEASE), 1, dat$SICDAT)
    siccheck<-any(dat$SICDAT == 1, na.rm=T)
    nosic<-which(dat$SICDAT==1)
    if(siccheck == T){
      print(paste0("<br> <ul> \textcolor{red}{ERROR: Missing information for disease. Check line(s) ", paste(nosic+1, collapse=" , "), "}", sep = " ", "</br> </ul>"))
    }else{ cat("<br> <ul> Disease status recorded </br> </ul>")
    }


    dat$SEXDAT<-NA
    dat$SEXDAT<-ifelse(dat$SPECCD_ID == 2550 & is.na(dat$SEXCD_ID), 1, dat$SEXDAT)
    sexcheck<-any(dat$SEXDAT == 1, na.rm=T)
    nosex<-which(dat$SEXDAT==1)
    if(sexcheck == T){
      print(paste0("<br> <ul> \textcolor{red}{ERROR: Missing information for sex. Check line(s) ", paste(nosex+1, collapse=" , "), "}",sep=" ", "</br> </ul>"))
    }else{ cat("<br> <ul> Sex recorded </br> </ul>")
    }

    dat$CONDAT<-NA
    dat$CONDAT<-ifelse(dat$SPECCD_ID == 2550 & is.na(dat$CONDITION_CD), 1, dat$CONDAT)
    concheck<-any(dat$CONDAT == 1, na.rm=T)
    nocon<-which(dat$CONDAT==1)
    if(concheck == T){
      print(paste0("<br> <ul> \textcolor{red}{ERROR: Missing information for condition. Check line(s) ", paste(nocon+1, collapse=" , "), "}", sep=" ", "</br> </ul>"))
    }else{ cat("<br> <ul> Condition recorded </br> </ul>")
    }
      
```


**12. Is the depth (in Fathoms) within a reasonable range ?**
```{r echo=FALSE, results = 'asis'}
dat$DEPTHCHECK <- NA
dat$DEPTHCHECK <- ifelse(dat$DEPTH <= 200, 0, ifelse(dat$DEPTH <= 300, 1, 2))

deepcheck_200 <- any(dat$DEPTHCHECK == 1, na.rm = TRUE)
deepcheck_300 <- any(dat$DEPTHCHECK == 2, na.rm = TRUE)
baddepth_200 <- which(dat$DEPTHCHECK == 1)
baddepth_300 <- which(dat$DEPTHCHECK == 2)

if (deepcheck_300) {
  print(paste0("  \textcolor{red}{ERROR: Depth on line(s) ", paste(baddepth_300 + 1, collapse = " , "), " is over 300 fathoms.}"))
}
if (deepcheck_200) {
  print(paste0("  \textcolor{orange}{WARNING: Depth on line(s) ", paste(baddepth_200 + 1, collapse = " , "), " is over 200 fathoms.}"))
}
if (!deepcheck_200 && !deepcheck_300) {
  cat("  Depths within reasonable range  ")
}

dat$DEPTHCHECK <- NULL
```


**13. Were any lobster kept below the MLS for the given LFA?**
```{r echo= FALSE, results = 'asis'}
      MLS=82.5
      dat$smallretained <-0

      if(unique(dat$COMAREA_ID) %in% c("L28","L29")){
        MLS=84 }

      dat$smallretained[which(dat$SPECCD_ID ==2550 & dat$FISH_LENGTH < MLS & dat$KEPT == 1)]<-1

      if(any(dat$smallretained ==1) ){
        ij<-which(dat$smallretained==1)
        print(paste0("<br> <ul> \textcolor{red}{ERROR:Lobsters kept below MLS. Check line(s) ", paste(ij+1, collapse=" , "), "}",sep = " ", "</br> </ul>"))
      }else{cat("<br> <ul> No small lobsters retained </br> </ul>")}

      dat$smallretained = NULL
  
```


**14. Were female between 114-124mm kept in LFA 31a?**
```{r echo = FALSE, results = 'asis'}
        dat$window<- 0
        dat$window<- ifelse(dat$COMAREA_ID %in% c(311) & dat$SEXCD_ID %in% c(2,3) & dat$SPECCD_ID == 2550  & dat$FISH_LENGTH %in% c(114:124) & dat$KEPT %in% c(1), 1, 0) 
        if(any(dat$window == 1)){
              ko<-which(dat$window ==1)
              print(paste0("<br> <ul> \textcolor{red}{ERROR:Lobsters kept between 114-124mm in 31a. Check line(s)", paste(ko+1, collapse=" , "), "}", sep = " ", "</br> </ul>"))
            } else {
              cat("<br> <ul> No window restricted lobsters were kept </br> </ul>")
      }
       dat$window = NULL
```


**15. Were v-notched lobster retained in prohibited LFAs?**
```{r echo = FALSE, results = 'asis'}
            dat$keepnotch<-0
       if(any(is.na(dat$KEPT))) dat$KEPT[which(is.na(dat$KEPT))] <- 0
              dat$keepnotch<- ifelse(dat$COMAREA_ID %ni% c("L27","L31A") & !is.na(dat$VNOTCH) & dat$KEPT == 1,1,0)
       if(any(dat$keepnotch ==1)){
              pl<- which(dat$keepnotch==1)
              print(paste0("<br> <ul> \textcolor{red}{ERROR:V-notched lobsters retained in prohibited LFA. Check line(s) ", paste(pl+1, collapse=" , "), "}", sep = " ", "</br> </ul>"))
          }else{
              cat("<br> <ul> No vnotched lobster retained in prohibited area </br> </ul>")
          }
        dat$keepnotch =NULL
```


**16. Is abundance greater than 1 for anything other than whelks, starfish, urchins?**
```{r echo = FALSE, results = 'asis'}
          dat$AMOUNT<-NA
          dat$AMOUNT<- ifelse((dat$SPECSCD_ID <= 1000 | dat$SPECCD_ID %in% c(2550,2513,2511,2531,2520,2526)) & (dat$ABUNDANCE > 1), 1, 0)

          amountcheck<- any(dat$AMOUNT ==1, na.rm=T)
          wrongamount<-which(dat$AMOUNT==1)
        if(amountcheck ==T){ 
              print(paste0("<br> <ul> \textcolor{red}{ERROR:Check Abundance. Error on line(s)", paste(wrongamount+1, collapse=" , "), "}", sep = " ", "</br> </ul>"))
            } else {
              cat("<br> <ul> Abundance is correct </br> </ul>") 
            }
        dat$AMOUNT<-NULL
```
 
 
**17. If species is not a berried lobster does it have clutch and egg categories filled out?**
```{r echo = FALSE, results = 'asis'}
          dat$BERRIED<-NA
          dat$BERRIED<- ifelse(dat$SPECCD_ID ==2550 & dat$SEXCD_ID %in% c(1,2) & c(!is.na(dat$CLUTCH) | !is.na(dat$EGG_STAGE)),1,0)
          notberried<- any(dat$BERRIED == 1, na.rm=T)
          noberries<-which(dat$BERRIED==1)
  if(notberried ==T){
          print(paste0("<br> <ul> \textcolor{red}{ERROR:Check SEX, CLUTCH, an/or EGG STAGE. Error on line(s) ", paste(noberries+1, collapse=" , "), "}", sep = " ", "</br> </ul>"))
          } else {
            cat("<br> <ul> Only berried females have egg and clutch information  </br> </ul>")
          }
    dat$BERRIED<-NULL
```


**18. If a lobster is berried is egg stage and clutch size recorded?**
```{r echo = FALSE, results = 'asis'}
          dat$BERRIES<-NA
          dat$BERRIES<- ifelse(dat$SPECCD_ID ==2550 & dat$SEXCD_ID== 3 & c(is.na(dat$CLUTCH) | is.na(dat$EGG_STAGE)),1,0)
          berried<- any(dat$BERRIES == 1, na.rm=T)
          noberried<-which(dat$BERRIES==1)
    if(berried ==T){
            print(paste0("<br> <ul> \textcolor{red}{ERROR:Check CLUTCH and/or EGG STAGE. Error on line(s) ", paste(noberried+1, collapse=" , "), "}", sep= " ", "</br> </ul>"))
          } else {
          cat("<br> <ul> Berried females have egg and clutch information </br> </ul>")
        }
dat$BERRIES<-NULL
```


**19. Do all crab species entries have length, sex and condition recorded?**
```{r echo = FALSE, results = 'asis'}
          dat$CRABBIE<-NA
          dat$CRABBIE<- ifelse(dat$SPECCD_ID %in% c(2513,2511,2531,2520,2526) & (dat$FISH_LENGTH < 1 | is.na(dat$FISH_LENGTH)) & (!dat$SEXCD_ID %in% c(1,2,3) | is.na(dat$SEXCD_ID)), 1, 0)
          crabinfo<- any(dat$CRABBIE ==1, na.rm=T)
          nocrab<- which(dat$CRABBIE ==1)
    if(crabinfo ==T){
                print(paste0("<br> <ul> <center> \textcolor{red}{ERROR:Check SEX and/or FISH LENGTH. Error on line(s) ", paste(nocrab+1, collapse=" , "), "}", sep= " ", "</br> </ul> </center>"))
          } else {
            cat("<br> <ul> All crabs have length and sex recorded </br> </ul>")
          }
      dat$CRABBIE<- NULL 

      dat$CCONDAT<-NA
      dat$CCONDAT<-ifelse(dat$SPECCD_ID %in% c(2513,2511,2531,2520,2526)  & is.na(dat$CONDITION_CD), 1, dat$CCONDAT)
      cconcheck<-any(dat$CCONDAT == 1, na.rm=T)
      noccon<-which(dat$CCONDAT==1)
    if(cconcheck == T){
              print(paste0("<br> <ul> \textcolor{red}{ERROR: Missing information for condition. Check line(s) ", paste(nocon+1, collapse=" , "), "}", sep= " ","</br> </ul>"))
      } else { 
        cat("<br> <ul> Condition recorded </br> </ul>")
    }
    dat$CCONDAT <- NULL
```


**20. Does anything other than a lobster have the notch category filled out?**
```{r echo = FALSE, results = 'asis'}
        dat$NOTCHED<- NA
        dat$NOTCHED<- ifelse(!dat$SPECCD_ID==2550 & !is.na(dat$VNOTCH),1,0)
        nonotch<- any(dat$NOTCHED==1, na.rm=T)
        notchless<- which(dat$NOTCHED ==1)
    if(nonotch ==T){
              print(paste0("<br> <ul> \textcolor{red}{ERROR:Check NOTCH on line(s) ", paste(notchless+1, collapse=" , "),"}", sep= " ", "</br> </ul>"))
        } else {
          cat("<br> <ul> Only lobster have notches </br> </ul>")
        }
    dat$NOTCHED<-NULL
```


**21. Do all Fish species entries have length, condition recorded?**
```{r echo = FALSE, results = 'asis'}
dat$FISHY <- NA
dat$FISHY <- ifelse(dat$SPECCD_ID < 1000 & (dat$FISH_LENGTH < 1 | is.na(dat$FISH_LENGTH)), 1, 0)
fishinfo <- any(dat$FISHY == 1, na.rm = TRUE)
nofish <- which(dat$FISHY == 1)
if (fishinfo == TRUE) {
    cat(paste0("<br> <ul> \\textcolor{red}{ERROR: Check FISH LENGTH on line(s) ", paste(nofish + 1, collapse = " , "), "} </br> </ul>"))
} else {
    cat("<br> <ul> All fish have length recorded </br> </ul>")
}
dat$FISHY <- NULL 

dat$CCONDAT <- NA
dat$CCONDAT <- ifelse(dat$SPECCD_ID %in% c(1:1000, 2513, 2511, 2531, 2520, 2526) & is.na(dat$CONDITION_CD), 1, dat$CCONDAT)
cconcheck <- any(dat$CCONDAT == 1, na.rm = TRUE)
noccon <- which(dat$CCONDAT == 1)
if (cconcheck == TRUE) {
    cat(paste0("\\textcolor{red}{ERROR: Missing information for CONDITION. Check line(s) ", paste(noccon + 1, collapse = " , "), "}"))
} else {
    cat("<br> <ul> All fish have condition recorded </br> </ul>")
}
dat$CCONDAT <- NULL

# New check for incorrect CONDITION_CD values
dat$INCORRECT_COND <- NA
dat$INCORRECT_COND <- ifelse(dat$SPECCD_ID < 1000 & dat$CONDITION_CD %in% c(1, 2, 3), 1, 0)
incorrect_cond_check <- any(dat$INCORRECT_COND == 1, na.rm = TRUE)
incorrect_cond_lines <- which(dat$INCORRECT_COND == 1)
if (incorrect_cond_check == TRUE) {
    cat(paste0("\\textcolor{red}{ERROR: Fish species have incorrect Condition Codes - Fish Condition can only be 0, 4, 5, 6, or 7. Check line(s) ", paste(incorrect_cond_lines + 1, collapse = " , "), "}"))
} else {
    cat("<br> <ul> All fish have correct condition codes </br> </ul>")
}
dat$INCORRECT_COND <- NULL
```


**22. What is the trap sampling frequency per string?**
```{r echo = FALSE, results = 'asis'}
trapnum<-as.data.frame(unique(cbind(dat$SET_NO,dat$TRAP_NO)))
if(any(!is.na(c(trapnum$V1)))){
trapnum<-trapnum[order(trapnum$V1,trapnum$V2),]
trapfreq<-aggregate(V2~V1, data=trapnum,FUN = function(x) mean(diff(x)))
trapfreq$test<-round(trapfreq$V2,0)
names(trapfreq)[1:2]<-c("String", "Frequency")
irrfreq<-which(trapfreq$Frequency != trapfreq$test)
trapfreq$test <-NULL
if(length(irrfreq)> 0){
  print(paste0("<br> <ul> \textcolor{red}{ERROR:Irregular trap sampling frequencies in string(s) ", trapfreq[irrfreq,"String"], "}", sep=" ", "</br> </ul>" ))
}
if(length(irrfreq)<nrow(trapfreq)){
  cat("<br> <ul> Trap sampling frequencies by string </br> </ul>")
  if(length(irrfreq)>=0)cat(paste0("<ul> One in ",  unique(trapfreq[-irrfreq,'Frequency']), " traps sampled per string </ul>"))
}
}
  
```


**23. What is the total number of traps sampled and total traps hauled**
```{r echo= FALSE, results = 'asis'}

sampled <- length(unique(paste(dat$TRAP_NO, dat$SET_NO, sep = "-")))

if (length(sampled) > 0) {
  cat(paste0("<br> <ul> Total number of traps sampled: ", sampled, "</br> </ul>"))
}

# Create a data frame with unique SET_NO and NUM_HOOK_HAUL
totaltrap <- unique(dat[, c("SET_NO", "NUM_HOOK_HAUL")])

# Check if the sum of NUM_HOOK_HAUL is less than the number of sampled traps
if (sum(totaltrap$NUM_HOOK_HAUL, na.rm = TRUE) < sampled) {
  cat("<br> <ul> <span style='color:red;'>ERROR: Check SET NO and NUM HOOK HAUL numbers do not add up to total traps sampled.</span> </br> </ul>")
} else {
  cat(paste0("<br> <ul> Total number of traps hauled: ", sum(totaltrap$NUM_HOOK_HAUL, na.rm = TRUE), "</br> </ul>"))
}
```


**24. What was the total number of lobsters and other species sampled?**
```{r echo=FALSE, results = 'asis'}
numlob<-length(which(dat$SPECCD_ID==2550))

if(length(numlob>0)){
  cat(paste0("<br> <ul> Total number of lobsters sampled: ", numlob, "</br> </ul>"))
      
}

numother<-length(which(dat$SPECCD_ID != 2550))

if(length(numother>0)){
  cat(paste0("<br> <ul> Total number of non lobsters sampled: ", numother, "</br> </ul>"))
}


numother<-length(unique(dat$SPECCD_ID))

if(length(numother>0)){
  cat(paste0("<br> <ul> Total number of species: ", numother, "</br> </ul>"))
  }
```


**Does the Trip count to Target?**
```{r echo=FALSE, results = 'asis'}
nums <- length(dat$SPECCD_ID)

if (nums > 0) {
  cat(paste0("  Total number of individuals sampled: ", nums, " "))
}

sampled <- length(unique(paste(dat$TRAP_NO, dat$SET_NO, sep = "-")))

if (sampled > 0) {
  cat(paste0("  Total number of traps sampled: ", sampled, " "))
}

ll <- unique(dat$COMAREA_ID)
lll <- ifelse(nchar(ll) == 3, 3, 4)
ll <- substr(ll, 2, lll)
mm <- as.numeric(substr(strsplit(nm, "-")[[1]][2], 3, 4))
out <- c()
i <- 'Not Enough'  # Initialize i with a default value

if (ll %in% c(33, 34)) {
  if (mm %in% c(11, 12, 4, 5)) {
    i <- ifelse(nums >= 300 | sampled >= 25, 'Good', 'Not Enough')
  }
  if (mm %in% c(1, 2, 3)) {
    i <- ifelse(nums >= 300 | sampled >= 50, 'Good', 'Not Enough')
  }
}

if (ll %in% c(35)) {
  if (mm %in% c(10, 11, 12, 5, 6, 7)) {
    i <- ifelse(nums >= 300 | sampled >= 25, 'Good', 'Not Enough')
  }
  if (mm %in% c(1, 2, 3, 4)) {
    i <- ifelse(nums >= 300 | sampled >= 50, 'Good', 'Not Enough')
  }
}

if (i == 'Good') {
  cat("  \\textcolor{green}{This trip will count toward targets.}  ")
} 
if (i == 'Not Enough') {
  cat("  \\textcolor{red}{This trip will NOT count toward targets.}  ")
}
```
  
  	